### 2020-06-03 writeup/setup.tex
sec 2

\section{Technical Tools using Random Matrix Theory}
\label{sec_main}

We begin by describing our problem setup more formally.
Then, we describe our main result for the bias-variance tradeoff of multi-task and transfer learning estimators in our setting.

%\subsection{Problem Setup}\label{sec_setup}

>>>>

\section{A Concentration Bound Generalizing Single-Task Settings}
\label{sec_main}

In this section we describe how \textit{task similarity}, \textit{sample size} and \textit{covariate shift} arise from the bias-variance tradeoff in the multi-task setting.
We illustrate how a natural quantity involving the spectrum of two random matrices arise, and then show a tight concentration bound for this quantity using random matrix theory.
